Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-18 paper.tex
a not great summary of SPM

        \note{pipeline description}
        A pipeline in PSOM, is a series of connected jobs, which can be
represented as a directed acyclic graph. The pipeline itself is implemented 
using the Matlab/Octave data type. Each job within the pipeline
is assigned a unique name. There is only one mandatory field in the job
description (command). The remaining four optional fields include the list input
files (files\_in), the list output files (files\_out), the list of files to be
deleted after execution (files\_clean) and any Octave or Matlab datatype
containing the remaining parameters necessary for job execution (opt).
Jobs in PSOM run in a protected environment where they only have access to the
parameters that are passed.

@@

        \subsection{limitations of PSOM}
    \section{SPM} 
        \subsection{summary} 
        \subsection{limitations of SPM}
    \section{Nexflow}
        \subsection{summary}
    \section{OpenMOLE}
        \subsection{summary} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}

>>>>

        \note{pipeline description}
        A pipeline in PSOM, is a series of connected jobs, which can be
represented as a (static?) directed acyclic graph. The pipeline itself is implemented 
using the Matlab/Octave data type. Each job within the pipeline
is assigned a unique name. There is only one mandatory field in the job
description (command). The remaining four optional fields include the list input
files (files\_in), the list output files (files\_out), the list of files to be
deleted after execution (files\_clean) and any Octave or Matlab datatype
containing the remaining parameters necessary for job execution (opt).
Jobs in PSOM run in a protected environment where they only have access to the
parameters that are passed.

@@

        \subsection{limitations of PSOM}
    \section{SPM and matlabbatch} 
        \note{This section may not make much sense. Have not really yet fully
understood matlabbatch}
        \subsection{summary} 
        SPM is a very popular neuroimaging toolkit, and as a result,
neuroimaging pipeline engines such as Nipype provide interfaces for it. SPM is
also equipped with its own neuroimaging pipeline engine known as
\textit{matlabbatch}. Similarly to PSOM and as its name suggest, it is written
in Matlab.

        \note{pipeline description}
        Pipelines in matlabbatch consist of a series of connected data
processing steps known as "modules" \note{DAG?? probably but not explicitly
listed anywhere}. All SPM modules, helper modules and their respective
dependencies can be defined using SPM's GUI \note{can probably also be done
through command-line}.

        For any matlabbatch job, it is possible to create a skeleton of it. A
skeleton is a Matlab script containing a commented list of necessary inputs at
the top and all code necessary to initialize and run the script. Before running,
the skeleton will need to be configured with the input names and other
necessary parameters.

        All configuration options can be set/changed by modifying the
\textit{cfg\_<type>} files.

        Defaults can be set within the configuration files, through a default
file, or in a \textit{.def} field for leaf nodes \note{terminal jobs???}. The
latter updates at the start of the new job execution whereas the former are
configured at the beginning of the SPM/matlabbatch startup.

        Virtual outputs represent the dependencies between jobs \note{unsure}.
They contain three paramaters of which only one is optional: sname, src\_output,
tgt\_spec. sname is the display name that will be stored in the dependecies
list, whereas src\_output is a subscript reference used to refer to the output
that is produced at runtime. The optional parameter, tgt\_spec, is a description
of the kind of inputs the outputs produced can be a dependency for. The virtual
output callbacks are evaluated when cfg\_(ex)branch, cfg\_choice and cfg\_repeat 
have the correct number of child nodes within all their in-tree nodes.

        \note{pipeline execution}
        Pipeline execution can be achieved either through the provided GUI or by
the command-line interface. The GUI, however, requires significant user
interaction, as the user must repeat the "Runs" command as many times as
necessary to reexecute the command on multiple data. The CLI, however, avoids
this with the help of its \textit{spm\_jobman} interface.

        The first step to running a batch pipeline is to perform the
initialization. This may include configuring the \textit{spm\_defaults.m} code
to run in command line and executing the \textit{spm(’defaults’, MODALITY)}
(where MODALITY represents the modality used in the pipeline) and
\textit{spm\_jobman(’initcfg’)}.

        After the intialization is complete, a job may be executed using the
\textit{spm\_jobman(’run’, job[, input1, input2 ...])} command. This command
requires the job names as well as its necessary inputs specified in the correct
order. The job can be specified as a variable, the name of a script that will
generate a job variable or a cell list containing a mixture of scripts and job
variables.

        \note{debugging and provenance}
        All batch scripts can be saved as a Matlab scripts. These scripts not
only contain the code that was executed, but also all input parameters. Should
any script fail in the process of executing, an error will be printed to the
Matlab console. If the user is using the GUI, the error output may also be saved
to a Matlab file.

        \subsection{limitations of SPM}
    \section{Nexflow}
        \subsection{summary}
    \section{OpenMOLE}
        \subsection{summary} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}
